Evaluating Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe using radiocarbon data

### 2019-03-28 review/answer_to_review.md

I was not aware of this work and added a paragraph in the introduction to reference it. It is indeed relevant.

> In the paper, it’s very high the amount of data, for which the archaeological information regarding the type of burial and funerary rite is lacking. At table 1, page 4, we can clearly detect that for 60% of the dates associated to cremation burials we have no information regarding the type of funerary structure. For 37% of the inhumations, no information about the funerary structure is available. Moreover, for 32% of the dataset (559 radiocarbon dates out of 1701) we do not have any kind of information regarding neither the funerary rite nor the burial structure. This lack of data obliges the author to consider carefully the results reached in the paper. It’s relevant to highlight all the biases of the prosed research and how the conclusion can be misleading due to the quality of available data. In particular, when the statistical analyses carried out on data aim to explore in the details the cultural distance among the different regions.

This is true and I tried to emphasise the limitations of the data in the discussion. The challenges are not confined on the amount of data, but also concern its meaning and origin. The supplementary remarks are extensively long to cover these problems.

@@

> Page 5, Column 1, Line 24. Perhaps worth making this a subsection?

I removed the simulation. See my reply above.

> Page 5, Column 1, Lines 24-60. I have several issues with this model. The idea here is to emulate the observed data so we can build expectations that can be directly compared against empirical patterns. But I do find several issues: 1) How is Ng=100 justified? This seems a somewhat arbitrary number for a parameter that is likely going to play a significant role in the amount of drift in the system? 2) I understand each time-step is 20 years. Why? I assume this is related to generation length but this ought to be discussed; 3) Is the model supposed to reach an equilibrium state? If this is the case I don’t think 70 time-steps and Ng=100 is sufficient for this. If the answer is no, the initial condition of the system shouldn’t be random and perhaps be informed from the empirical data.

I will consider this important questions in a future publication.

### 2019-03-28 article/02_Materials_and_Methods.Rmd
figure and table captions

```{r gprcrosstab, echo=FALSE, tidy=FALSE}
load("../analysis/data/output_data/gprcrosstab.RData")
colnames(gprcrosstab)[1:2] <- c("Region", "Burial type")
gprcrosstab %>% 
  knitr::kable(
    caption = "Burial rite distribution in the active grave dataset.",
    format = "latex",
    booktabs = T,
    escape = F,
    align = "l"
  ) %>%
  kableExtra::kable_styling(
    full_width = T,
    font_size = 9,
    latex_options = "hold_position"
  ) %>%
  kableExtra::add_header_above(c(" " = 1, " " = 1, "Burial construction" = 3)) %>%
  kableExtra::column_spec(1, width = "2 cm") %>%
  kableExtra::column_spec(2, width = "1.5 cm") %>%
  kableExtra::column_spec(3:5, width = "0.8cm") %>%
  kableExtra::collapse_rows(1, row_group_label_position = "identity", valign = "top") %>%   kableExtra::row_spec(row = 25:27, align = "center", bold = T)

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/development_burial_type.jpeg}
\caption{\label{development_burial_type}Regional distribution time series of the variable \textit{burial type} with the absolute amount (\textbf{A}) and proportion (\textbf{B}) of grave types. The x-axis shows the time, the y-axis the amount or the percentage shares of graves. The individual plots are separated by region, and each region is featured by a small map according to Figure \ref{map_regions} A. The order of the regions follows a southeast-\\northwest direction.}
\end{figure}

>>>>

```{r gprcrosstab, echo=FALSE, tidy=FALSE}
load("../analysis/data/output_data/gprcrosstab.RData")
colnames(gprcrosstab)[1:2] <- c("Region", "Burial type")
gprcrosstab %>% 
  knitr::kable(
    caption = "Burial rite distribution in the active grave dataset. The order of the regions follows a southeast-northwest direction.",
    format = "latex",
    booktabs = T,
    escape = F,
    align = "l"
  ) %>%
  kableExtra::kable_styling(
    full_width = T,
    font_size = 9,
    latex_options = "hold_position"
  ) %>%
  kableExtra::add_header_above(c(" " = 1, " " = 1, "Burial construction" = 3)) %>%
  kableExtra::column_spec(1, width = "2 cm") %>%
  kableExtra::column_spec(2, width = "1.5 cm") %>%
  kableExtra::column_spec(3:5, width = "0.8cm") %>%
  kableExtra::collapse_rows(1, row_group_label_position = "identity", valign = "top") %>%   kableExtra::row_spec(row = 25:27, align = "center", bold = T)

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/development_burial_type.jpeg}
\caption{\label{development_burial_type}Regional distribution time series of the variable \textit{burial type} with the absolute amount (\textbf{A}) and proportion (\textbf{B}) of grave types. The x-axis shows the time, the y-axis the amount or the percentage shares of graves. The individual plots are separated by region, and each region is featured by a small map according to Figure \ref{map_regions} A. $n$ in the facet labels equals the total number of available dates with information for the variable (cf. Table \ref{tab:gprcrosstab}).}
\end{figure}
